\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[backend=bibtex]{biblatex}


\RequirePackage{titlesec}
\RequirePackage{tikz}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

% LONG or SHORT Resume
\newif\iflong
\longtrue
%\longfalse

% Create a tag
% Usage: \cvtag{<tag label>}
\definecolor{darkGrey}{HTML}{989898}
\newcommand{\cvtag}[1]{%
  \tikz[baseline]\node[anchor=base,draw=black!70,rounded corners=0.5ex,
  inner xsep=1ex,inner ysep =0.7ex,text height=1.3ex,text depth=.25ex]{#1};
}

\newcommand\tags[1]{
  \footnotesize{\foreach \n in {#1}{\cvtag{\texttt{\n}}}}
}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ \textbf{--} #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithTags}[3]{
  \item\small{
    \textbf{#1}{ \textbf{--} #2 \\ \underline{Keywords:} {#3} \vspace{1pt}} 
  }
}

\newcommand{\resumeItemNoHeader}[1]{
  \item\small{
    { #1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubItemNoHeader}[1]{\resumeItemNoHeader{#1}\vspace{-4pt}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingSmallNoItalics}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & \small#2 \\
      {\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\referenceItem}[3]{
  \vspace{-2pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {#1} & #3 \\
      \textit{\small#2} \\
    \end{tabular*} %\vspace{-5pt}
}

\newcommand{\referenceItemNoEmail}[2]{
  \vspace{-2pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {#1}  \\
      \textit{\small#2} \\
    \end{tabular*} %\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://anilyelam.com/}{\Large Anil Yelam (Under Construction)}} \\
  \href{http://anilyelam.com}{http://anilyelam.com} & 
  \underline{Email}: \href{mailto:ayelam AT ucsd.edu}{ayelam AT ucsd.edu}       \\
  
\end{tabular*}

%----------STATEMENT-----------------
\section{Statement}
{\small I am broadly interested in building/improving systems 
and networking stacks that underpin modern cloud platforms. 
At UC San Diego, I am advised by \textbf{Prof.\ Alex Snoeren} 
and my current work focuses on developing systems for remote/
disaggregated memory architectures.} \vspace{-5pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheadingSmallNoItalics
  {University of California San Diego}{San Diego, CA}
  {PhD in Computer Science; GPA: \textbf{3.96}} 
  {Fall 2018 - Present}
\resumeSubheadingSmallNoItalics
  {Indian Institute of Technology Kharagpur}{Kharagpur, India}
  {B.Tech. in Computer Science and Engineering;  GPA: \textbf{3.83} (9.58/10.0)}
  {Aug. 2010 -- July. 2014}
  \resumeSubHeadingListEnd

%-----------Publications-----------------
\section{Publications}
    \resumeSubHeadingListStart

    \resumeSubItem{\href{https://dl.acm.org/doi/pdf/10.1145/3387514.3405895}
    {\textbf{SmartNIC Performance Isolation with FairNIC: 
      Programmable Networking for the Cloud}}}

    {\vspace{2pt}
    Stewart Grant\textbf{*}, \textbf{Anil Yelam*}, Maxwell Bland 
      and Alex C. Snoeren. \textit{SIGCOMM ’20}}
      
    {\vspace{-2pt} (\textbf{*}Co-first authors)}
    
    \resumeSubItem{\href{https://dl.acm.org/doi/pdf/10.1145/3387514.3405895}
    {\textbf{Covert Communication In The Cloud With Lambdas}}}

    {\vspace{2pt}
    \textbf{Anil Yelam}, Shibani Subbareddy, Keerthana Ganesan, 
      Stefan Savage and Ariana Mirian. \textit{The Web Conference ’21}}
    
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {UC San Diego}{San Diego, CA}
      {Graduate Researcher, Advisor: Prof. Alex Snoeren}{Oct 2018 - Present}
      \resumeItemListStart
      \resumeItemWithTags{High-Performance CPU scheduling on Remote Memory  (In Progress)}
          {Memory disaggregation decouples and pools CPU and DRAM in rack 
          to provide resource efficiency benefits but it comes at the cost of application 
          performance due to increased memory latencies. I'm working on a CPU scheduler 
          that hides this cost for highly-parallel applications while retaining traditional 
          programming abstractions for backwards compatibility.}
          {Disaggregated Memory, CXL, Remote Paging, Userfaultfd, Shenango, Memcached, LinuxMM}
      \resumeItemWithTags{NIC-assisted object serialization for managed runtimes}
          {Serialization consumes a significant portion of computation in modern 
          data platforms like Spark. I explored the feasibility of offloading this work 
          to NICs using their DMA capabilities to gather and serialize Java objects 
          during transmit.}
          {Apache Spark, RDMA, PCIe \& DMA concepts, JVM development}
      \resumeItemWithTags{Covert channel in Cloud with Serverless functions}
          {Demonstrated the potential for a covert channel in the Cloud using serverless 
          functions (lambdas) on major clouds like AWS and Azure. We developed a new co-residence 
          detection technique for lambdas (a la MAC protocols) that breaks cloud isolation
          to detect lambdas running on the same underlying server, enabling the covert 
          communication.}
          {Cloud security, Lambdas, Covert channels, Cloud cartography}
      \resumeItemWithTags{Multi-tenancy in Programmable NICs}
          {Offloading computation to programmable NICs offers a scalable way for network 
          processing at higher (40\&100G) network speeds. In this work, we developed 
          performance isolation mechanisms on these NICs to enable these offloading benefits for 
          tenant VMs in the cloud, enabling easier adoption of these NICs in the Cloud. }
          {SoC SmartNICs, NIC Drivers \& Firmware, Linux SKB, DPDK, C, Python}
\iflong
       \resumeItemWithTags{Analyzing Network Performance of Spark}
          {The goal was to understand efficiency of data analytics frameworks like 
          Apache Spark and Giraph at converting extra network bandwidth into job speedup.}
          {Apache Spark, Apache Giraph, Hadoop, Java GC Tuning, Python}
\fi
        \resumeItem{Teaching Assistant} {Graduate Distributed Systems, 2020}
      \resumeItemListEnd

    \resumeSubheading
      {IIT Kharagpur}{Kharagpur, India}
      {Undergraduate Researcher, Advisor: Prof. Arobinda Gupta}{Summer 2013 - 2014}
      \resumeItemListStart
        \resumeItemWithTags{(Thesis) Event Delivery in Vehicular Networks}
          {Developed efficient heuristics for the (NP-hard) event delivery 
          in vehicular networks with minimum delay, where events are delivered to 
          vehicles moving through a city through road-side units with limited event capacity. 
          Evaluated the performance of these heuristics over Tokyo city traffic patterns.}
          {MANETs, Pub/Sub Messaging, C, NP-Hard, Biobjective Optimization}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


\section{Industry Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {VMware Research}{San Jose, CA}
      {Research Intern, Mentors: Radhika Niranjan Mysore, Marcos K. Aguilera}{2021}
        \resumeItemListStart
        \resumeItem{User-level threading framework for disaggregated memory}
        {As a first-step towards high-performance CPU scheduling in novel rack design 
        with disaggregated memory, I have integrated and benchmarked the 
        performance of a traditional user thread framework (Shenango) with a transparent 
        disaggregated memory system that uses remote paging. The results motivated a 
        need for new scheduler design more suited for the disaggregated setting.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Microsoft (Azure)}{Seattle, WA}
      {Software Engineer}{Dec  2014 - Jul 2018}
      \resumeItemListStart
        \resumeItem{Azure SQL VM}
          {Developed a control plane for provisioning SQL Server Linux VMs and  
          SQL Server Availability Groups on Microsoft Azure. This included building 
          highly available and scalable services that are deployed to all Azure regions 
          and offer four 9's availability for provisioning and management of these resources.}
        \resumeItemWithTags{Azure SQL Database}
          {Was part of Azure Database team that offers SQL Server Database on PaaS 
          and IaaS platforms on Microsoft Azure, where I developed and maintained services 
          that support a range of features for Azure SQL Database like automated performance 
          optimizations for user databases.}
          {Azure VMs, SQL, Failover Groups, C\#, C++, Python, Linux, Azure Service Fabric, SOA}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon}{Hyderabad, India}
      {Summer Intern}{2013}
      
  \resumeSubHeadingListEnd


%-----------AWARDS-----------------
\section{Awards and Achievements}
  \resumeSubHeadingListStart
    \resumeSubItemNoHeader
      {\textbf{Institute Silver Medal} and \textbf{Bigyan Sinha Prize} for the best academic performance at IIT Kharagpur, 2014.}
    \resumeSubItemNoHeader
      {Top 0.1\% in top-tier engineering entrance exams in India (JEE, AIEEE) that saw over a million applicants, 2010.}
    \resumeSubItemNoHeader
      {Multiple promotions during the three years at Microsoft for exceptional performance in the Azure Database team.}    
    \resumeSubItemNoHeader
      {\textbf{Patent} for Automated Database Index Recommendations for improvements in Azure SQL Database, 2015.}
  \resumeSubHeadingListEnd


%
%--------SKILLS------------
\section{Technical Skills (TODO)}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
     \hfill
     \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
   }
 \resumeSubHeadingListEnd

%
%--------COURSEWORK------------
\section{Relevant Coursework}
 \resumeSubHeadingListStart
    \resumeItem{Graduate}
    {Operating Systems, Distributed Systems, Accelerator Design, Data 
    Systems for ML, Computer Networks, Embedded Systems, Computer Security, 
    Programming Languages}
    \resumeItem{Undergraduate}
    {Algorithms, Advanced Graph Theory, Compilers, Computer Networks, 
    Computer Architecture, Distributed Systems, Formal Languages, 
    Foundations of Cryptography, Information Retrieval, Machine Learning, 
    Operating Systems, Speech and Natural Language Processing}
 \resumeSubHeadingListEnd

%
% --------REFERENCES------------
\section{References}
    \referenceItemNoEmail
    {Prof. Alex Snoeren}
    {University of California San Diego}
    \referenceItemNoEmail
    {Prof. Arobinda Gupta}
    {Indian Institute of Technology Kharagpur}

%-------------------------------------------
\end{document}