\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[backend=bibtex]{biblatex}


\RequirePackage{titlesec}
\RequirePackage{tikz}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands

% LONG or SHORT Resume
\newif\iflong
\longtrue
%\longfalse

% Create a tag
% Usage: \cvtag{<tag label>}
\definecolor{darkGrey}{HTML}{989898}
\newcommand{\cvtag}[1]{%
  \tikz[baseline]\node[anchor=base,draw=black!70,rounded corners=0.5ex,
  inner xsep=1ex,inner ysep =0.7ex,text height=1.3ex,text depth=.25ex]{#1};
}

\newcommand\tags[1]{
  \footnotesize{\foreach \n in {#1}{\cvtag{\texttt{\n}}}}
}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ \textbf{--} #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithTags}[3]{
  \item\small{
    \textbf{#1}{ \textbf{--} #2 \\ \underline{Keywords:} {#3} \vspace{1pt}} 
  }
}

\newcommand{\resumeItemNoHeader}[1]{
  \item\small{
    { #1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubItemNoHeader}[1]{\resumeItemNoHeader{#1}\vspace{-4pt}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingSmallNoItalics}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & \small#2 \\
      {\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingSmallNoBold}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \small#2
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\referenceItem}[3]{
  \vspace{-2pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {#1} & #3 \\
      \textit{\small#2} \\
    \end{tabular*} %\vspace{-5pt}
}

\newcommand{\referenceItemNoEmail}[2]{
  \vspace{-2pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {#1}  \\
      \textit{\small#2} \\
    \end{tabular*} %\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://anilyelam.com/}{\Large Anil Yelam}} \\
  \href{http://anilyelam.com}{http://anilyelam.com} & 
  \underline{Email}: \href{mailto:ayelam AT ucsd.edu}{ayelam AT ucsd.edu}       \\
  
\end{tabular*}

%----------STATEMENT-----------------
\section{Statement}
{\small I am broadly interested in building/improving systems 
and networking stacks that underpin modern cloud platforms. 
At UC San Diego, I am advised by \textbf{Prof.\ Alex Snoeren} 
and my current work focuses on developing systems for remote/
disaggregated memory architectures.} \vspace{-5pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheadingSmallNoItalics
  {University of California San Diego}{San Diego, CA}
  {PhD in Computer Science} 
  {Fall 2018 - Present}
\resumeSubheadingSmallNoItalics
  {Indian Institute of Technology Kharagpur}{Kharagpur, India}
  {B.Tech. in Computer Science and Engineering}
  {Aug. 2010 -- July. 2014}
  \resumeSubHeadingListEnd

%-----------Publications-----------------
\section{Publications}
    \resumeSubHeadingListStart

    \resumeSubItem{\href{https://dl.acm.org/doi/pdf/10.1145/3387514.3405895}
    {\textbf{SmartNIC Performance Isolation with FairNIC: 
      Programmable Networking for the Cloud}}}

    {\vspace{2pt}
    Stewart Grant\textbf{*}, \textbf{Anil Yelam*}, Maxwell Bland 
      and Alex C. Snoeren. \textit{SIGCOMM ’20}}
    {\vspace{-2pt} (\textbf{*}Co-first authors)}
    
    \resumeSubItem{\href{https://dl.acm.org/doi/pdf/10.1145/3387514.3405895}
    {\textbf{Covert Communication In The Cloud With Lambdas}}}

    {\vspace{2pt}
    \textbf{Anil Yelam}, Shibani Subbareddy, Keerthana Ganesan, 
      Stefan Savage and Ariana Mirian. \textit{The Web Conference ’21}}
    
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Recent Projects}
  \resumeItemListStart
  \resumeItemWithTags{High-Performance CPU scheduling on Remote Memory  (In Progress)}
      {Memory disaggregation decouples and pools CPU and DRAM in rack 
      to provide resource efficiency benefits but it comes at the cost of application 
      performance due to increased memory latencies. I'm working on a CPU scheduler 
      that hides this cost for highly-parallel applications while retaining traditional 
      programming abstractions for backwards compatibility.}
      {Disaggregated Memory, CXL, Remote Paging, Userfaultfd, Shenango, Memcached, LinuxMM}
  \resumeItemWithTags{NIC-assisted object serialization for managed runtimes}
      {Serialization consumes a significant portion of computation in modern 
      data platforms like Spark. I explored the feasibility of offloading this work 
      to NICs using their DMA capabilities to gather and serialize Java objects 
      during transmit.}
      {Apache Spark, RDMA, PCIe \& DMA concepts, JVM development}
  \resumeItemWithTags{Covert channel in Cloud with Serverless functions}
      {Demonstrated the potential for a covert channel in the Cloud using serverless 
      functions (lambdas) on major clouds like AWS and Azure. We developed a new co-residence 
      detection technique for lambdas (a la MAC protocols) that breaks cloud isolation
      to detect lambdas running on the same underlying server, enabling the covert 
      communication.}
      {Cloud security, Lambdas, Covert channels, Cloud cartography}
  \resumeItemWithTags{Multi-tenancy in Programmable NICs}
      {Offloading computation to programmable NICs offers a scalable way for network 
      processing at higher (40\&100G) network speeds. In this work, we developed 
      performance isolation mechanisms on these NICs to enable these offloading benefits for 
      tenant VMs in the cloud, enabling easier adoption of these NICs in the Cloud. }
      {SoC SmartNICs, NIC Drivers \& Firmware, Linux SKB, DPDK, C, Python}
  \resumeItemListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheadingSmallNoBold
  {Research Collaborator, VMware}{Summer 2021 -- Present}
\resumeSubheadingSmallNoBold
  {Research Intern, VMware (\textbf{Mentors:} Radhika Niranjan Mysore, Marcos K. Aguilera)} {Summer 2021}
\resumeSubheadingSmallNoBold
  {Teaching Assistant, Graduate Distributed Systems}{Spring 2020}    
\resumeSubheadingSmallNoBold
  {Software Engineer, Microsoft Azure}{2014 -- 2018}
\resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Awards and Achievements}
  \resumeSubHeadingListStart
    \resumeSubItemNoHeader
      {\textbf{Institute Silver Medal} and \textbf{Bigyan Sinha Prize} for the best academic performance at IIT Kharagpur, 2014.}
    \resumeSubItemNoHeader
      {Top 0.1\% in top-tier engineering entrance exams in India (JEE, AIEEE) that saw over a million applicants, 2010.}
    \resumeSubItemNoHeader
      {Multiple promotions during the three years at Microsoft for exceptional performance in the Azure Database team.}    
    \resumeSubItemNoHeader
      {\textbf{Patent} for Automated Database Index Recommendations for improvements in Azure SQL Database, 2015.}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}